I am going to try and speed this along a little bit though since I read that the best man isn't supposed to drink until after he has given the best man speech and well, a drink is starting to sound pretty good right about now.

So onto my relationship with Mitch. I first met Mitch in the early nineties. Sorry for the insider there, for those of you who don't know me, I’m Mitchell’s BEST brother. I also happen to be his only brother but I think BEST has a better ring to it. And just to get things straight, I'm also the OLDER brother. I’m not Mitchell’s twin, and I am definitely not his younger brother. I don't know why but people always think they're going to impress me and Mitch by guessing which one of us is older. News flash for those of you who do this, you are almost never right. It happens so infrequently that I can probably count the number of times on one hand. Now, I suppose if I can keep this up for the next 30 years then I'll have the last laugh. Just you wait Mitchell. To add insult to injury Mitchell has ALWAYS been taller than me. Well, that's not completely true. There was a week in high school where I was both tall and taller than Mitchell. Unfortunately that didn't last.

Now that we've got that out of the way, Mitch has been around for 22 almost 23 years and in that time me and him have barely spent more than four months apart in a consecutive time period.
Right from when Mitch was born we've pretty much been glued at the hip. Well, except for that time when we were about two and four and Mitchell left little floating surprise in the tub. It took me a little while to get over that one.

Okay, so fast forward a little bit, I can honestly say that I've spent more time with Mitchell than anyone else that I have ever met. We always used to spent our entire weekend and most of the weekday after school together. No mat
ter how bad of a day I had at school Mitchell was always there for me when I got home. We also worked as a united force against the parents, powerless alone, but together, well still powerless. But doing chores was a lot more fun when I did them with Mitch.

We did lots of after school and summer activities as well. In the summer we used to have a tonne of fun swimming in Okanagan lake and going for hikes on the weekend when we were out on the boat. In fact, the only thing I remember not liking about the boat was this pair of blue shorts that dad used to wear. They were all torn and they had holes in them, but dad loved that pair of shorts. And he'd only put them on when we were out on the boat because he didn't want other people to see him in them, but he didn't think anything of me and Mitch. Actually, when I was going through some of our old family photos I found a picture where both me and Mitchell (we couldn't have been much older than 4 and 6) were both wearing that pair of shorts at the same time. And there would have been room to fit one more of us in those shorts. I remember brainstorming different ways of "disappearing" those shorts without dad finding out but I think dad eventually got rid of them himself.

During the winter season Mitchell was my best skiing and snowboarding buddy. I remember we used to play what was basically a game of tag in the trees when we were snowboarding. Looking back on that now, that was actually pretty dangerous. I also remember when we were really little we used to try and bribe the ski lift with cookies when it would stop moving. I think it got wise to us eventually because it hasn't worked for a few years.

We also went on quite a few memorable family holidays. I recall on one holiday we would always go snorkelling off the end of a dock that was near our place. There was a barracuda that lived right under that dock (if you've never seen a Barracuda before, they're basically look like a long tube but about a third of their body is just their head with a whole bunch of big teeth sticking out) and when dad first saw him there he named him Hermie. So every time we'd go snorkelling we'd just wave to Hermie and go on snorkelling. On another trip we both went to Ocean school where we learned all about different species of fish and how to identify them. That trip was just snorkelling though, but on a subsequent trip both me and Mitchell got our diving certificates. I believe Mitch was 10 at the time and they had just recently lowered the minimum age for getting your diving certificate. From there we went on a bunch of dives and we've got pictures of Mitchell petting a six-foot moray eel as it swam through his legs. I'm pretty sure we also ended up petting nursing sharks on that dive.

So fast forwarding again. I moved out to Calgary for University after high school and I was there two years before Mitchell came and joined me. I have to say the hardest part of going to University was spending the first two years without Mitch. Once he moved out he spent his first term in residence and then decided to move in with me. From there we lived together for the next four years so I happen to know a little something about what it's like living with Mitchell.

So I should disclose I never really lived completely alone with Mitchell. I actually lived with a person I like to call MuhBethany because even though Bethany wasn't there Mitchell was constantly on the phone texting her.

I remember that after Mitchell started his relationship with Bethany he had to get an unlimited texting plan. Telus got ripped off on that deal. Mitchell also always made time to give Bethany a call before he went to bed, even the before exams or after working on long assignments. I would just like to recognize how difficult it is to pull off a long distance relationship like that, very impressive.

At this point I should probably apologize for the long-windedness of this speech. Those of you who know me probably aren't surprised. I recall talking with Mitchell sometimes he kind of looks at me, but he's not really looking at me. I think he uses my ear as a staring point so it looks like he's still listening, but deep down I know that he is off in another world somewhere. When I'm talking with you Mitchell, where is it that you go? Don't answer that.

Okay so I know you aren't supposed to give advice during the best man speech but too bad I'm the one with the mike. So, Bethany before you start complaining about what it's like living with Mitchell, consider that the version of Mitchell your getting is Mitchell 2.0. It took a lot of work to get him to where he is now. Although I must admit that Mitchell is doing a really good job of getting your new place ready here in Kelowna ready for you after your honeymoon. So the first thing I should mention is that Mitch doesn't like making phone calls, and Bethany you probably know that already. He claims that he is better at it now but I've yet to see a difference. Just to give you an example, me and Mitchell spent almost a month with the oven on heating the house because the heating in the house died and I always seemed to be home when it was working. Eventually I made the call.

Another heads up, if Mitch is busy with something, he probably isn't going to do the dishes. Even if you give him all day. Trust me Bethany I've tried. Perhaps you'll have better luck though since you have *COUGH* ways to persuade him. If that does work by the way I would like to know because I tried everything.

The last last piece of advice is try to not sweat the small stuff. The biggest fight me and Mitchell ever had at our place in Calgary was over a spoon that one of us wanted. I don't even remember which one of us wanted it, I just remember how mad we got. Apparently that sort of thing isn't uncommon. My parents apparently fought quite a bit over one very small thing when they first moved in together. Apparently my father is very particular about the way his toothpaste is squeezed. Apparently the correct way is to roll it up from the bottom, and Mom would just squeeze from the middle. Today they each have their own separate toothpaste. So Mitchell, go and get a good engineering job and live a little. Buy two tubes of toothpaste.

On the subject of engineering, I saw Mitchell at his ring ceremony and I know how proud he is to have his engineering ring. It's amazing to me how many different ways Mitchell can change the conversation so he gets to bring up that ring. I also know that he is even more proud of the new ring he received, and I know that he is even more proud to be with you today Bethany. I'd also like to thank you because I know that you make my brother happy in a way that I never could.

Okay so I've missed something here. Oh right, the proposal. So shortly after Mitchell proposed to Bethany he gave me a call, and I can still remember how excited he was. I recall though that he was very disappointed to hear my very nonchelant reply. I think I just said "okay", like that.

So in order to understand why I wasn't more excited you have to realize that Mitchell had been talking about marrying Bethany for a very long time and I had basically considered it to be a done deal two years ago. So I'm formally apologizing for not being more surprised by the fact that it took you four years to propose. That's the difference between me and Mitch. On the one hand you have me frantically finishing off this speech last night and then you have Mitch meticulously planning his proposal for months and months. Putting the ring in a kinder-surprise? That is very Mitchell.

I'm also very pleased to be welcoming Bethany to our family. I couldn't ask for a better sister in-law. And, I'd just like I'm sorry for the last name. You've been spoiled with a last name like Edwards, be prepared to be called Mrs. Koopka, Mrs. Kopke, Mrs. Kopeke. So do us all a favour Bethany, treasure those few times when someone does get your name correct. For all of us poor Kopeks.

On a more serious note, I just want to say something about how passionate you are about your art. It first became apparent shortly after I first met you, in everything that you do. You express your artistic ability through how you do your hair, how you meticulously plan your clothes, and I can see it in everything you have done today. Your dress, your hair, the brides maids dresses (and a shout out to Lois as well who made the bridges maids dresses. I'm not surprised that your so good at art after seeing what your mother does as well.), and these awesome suspenders. I get to keep these after right? Anyway I just wanted to acknowledge the amazing job you've done today.

So getting close to drink time, I might have trouble with this part so try and bear with me. Mitch, I know that I don't say it very often but your my best friend. I know that I'll be seeing less of you now but it puts a big smile
on my face knowing how happy your going to be living with Bethany. And Bethany, I'm so glad to have you as (can I call you) a sister? Anyway, I should just say that I love you both Mitchell and Bethany. Mom made me say that.

So a toast to Bethany and Mitchell, I don't need to hope, I know you both will have a long and happy marriage.
